Delivering Reliable Software in the European Scientific Arena: Evolution of Methodologies and New Trend Analysis

### 2018-01-15 paper-ieee-trans.tex
Table II modified and intro of section II rephrased.

\documentclass[journal]{IEEEtran}
\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}

@@

In the following we provide an overview of the main EC-projects that have dealt with 
the issue of software reliability. Table \ref{tab:eup} shows the various projects 
with their logo, short name, long name and duration.

@@

\subsection{Features on software reliability in EC-projects}

In the following we summarize the features on software reliability in the aforementioned EC-projects.
Table \ref{tab:feat} shows the various projects 
with their features: the symbol $\surd$ crosses project and feature.

\begin{table*}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEE I, II, III & ETICS 1, 2 & EMI & EGI-Inspire & EGI Engage & INDIGO-DataCloud\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Build/Test Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&&\\
Automatic Certification Tool&&&$\surd$&&$\surd$&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&&$\surd$&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
\hline
\hline
\end{tabular}
\end{table*}

>>>>

\documentclass[journal]{IEEEtran}
\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}
\usepackage{adjustbox}

@@

The EC projects considered in this text are listed chronologically in Table
\ref{tab:eup}. In most cases, each project paved the way of the subsequent projects,
following a logic evolution in which the quality and reliability of software have
increasingly had a more significant role. Experiences gathered during the 
course of each project support this fact and, as it is shown in Table \ref{tab:feat},
latest projects are the most committed in terms of software reliability awareness.
This table summarizes the topics addressed in the following sections, highlighting 
the commonalities and specific features on software reliability.

@@

\begin{table}[!h]
%% increase table row spacing, adjust to taste
\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
\caption{Features on software reliability in EC-projects}
\label{tab:feat}
\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
\begin{adjustbox}{max width=0.5\textwidth}
\begin{tabular}{llllllll}
\hline
\hline
Feature & DataGrid & EGEE I, II, III & ETICS 1, 2 & EMI & EGI-Inspire \& Engage & INDIGO-DataCloud\\
\hline
\hline
Architecture Task Force&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Communication Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Requirements Handling&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Agile Methodologies&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Source code inspection&&&&$\surd$&&$\surd$\\
Build/Testing Management Procedure&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
Software Product Metrics&$\surd$&$\surd$&$\surd$&&$\surd$&$\surd$\\
Quality Criteria Definition&&&$\surd$&$\surd$&$\surd$&$\surd$\\
%Manual Certification Procedure&$\surd$&$\surd$&&$\surd$&&\\
Automatic Certification&&&$\surd$&&$\surd$&$\surd$\\
Auto-generated Documentation&&$\surd$&$\surd$&$\surd$&$\surd$&$\surd$\\
DevOps practices adoption (CI, CD)&&&&&&$\surd$\\
\hline
\hline
\end{tabular}
\end{adjustbox}
\end{table}
